---
title: "p8105_hw5_jh4617"
author: "Junjie Hu"
date: "2023-11-11"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r echo = FALSE}
library(tidyverse)
library(purrr)
```

# Problem 1

## Imported data, created `city_state` variable
```{r}
homicide_df =
  read.csv("homicide-data.csv")|>
  janitor::clean_names() |>
  mutate(city_state = paste(city, state, sep = ",")) |>
  filter(city_state != "Tulsa,AL") 
```

The raw data obtains `r nrow(homicide_df)` observations and `r ncol(homicide_df)` variables, including `r names(homicide_df)`.

## Summarized with cities
```{r}
homicide_df |>
  group_by(city) |>
  summarize(n = n()) |>
  knitr::kable()

homicide_df |>
  filter(disposition %in% c ("Closed without arrest", "Open/No arrest")) |>
  group_by(city) |>
  summarize(n = n()) |>
  knitr::kable()
```

## Estimated the proportion of homicide that are unsolved
```{r}

city_homicide_df = 
  homicide_df |>
  group_by(city, city_state) |>
  summarize(unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest")),
            total = n())

baltimore_test_df = 
  prop.test( 
    x = filter(city_homicide_df, city_state == "Baltimore,MD") %>% pull(unsolved),
    n = filter(city_homicide_df, city_state == "Baltimore,MD") %>% pull(total)) 

  broom::tidy(baltimore_test_df)

```

## Proportion for each cities
```{r}
test_results = 
  city_homicide_df |> 
  ungroup()|>
  mutate(
    prop_tests = map2(unsolved, total, \(x, y) prop.test(x = x, n = y)),
    tidy_tests = map(prop_tests, broom::tidy)) |> 
  select(-prop_tests) |>
  unnest(tidy_tests) |>
  select(city_state, estimate, conf.low, conf.high) |>
  mutate(city_state = fct_reorder(city_state, estimate))
```

Create plots
```{r}
test_results |>
  mutate(city_state = fct_reorder(city_state, estimate)) |>
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


# Problem 2

## Imported and combined files 
```{r}

file_list = 
  list.files(path = "data", full.names = TRUE) 

load_files = function(x){
  
  arm =
    str_extract(x, "con|exp")
  
  id = 
    str_extract(x, "\\d{2}")
  
data = 
    read.csv(x) |>
    janitor::clean_names()|>
    mutate(arm = arm, id = id)
    
}

output = 
  map(file_list, load_files) 

combined_df = 
  bind_rows(output) |>
  pivot_longer(
    week_1:week_8,
    names_to = "weeks",
    values_to = "values"
  )
```

## Made a spaghetti plot
```{r}
combined_df |>
  mutate(arm_id = paste(arm, id, sep = "-")) |>
  ggplot(aes(x = weeks, y = values, group = arm_id, color = arm)) +
  geom_line() +
    labs(title = "Plot of Observations Over Time",
       x = "Weeks",
       y = "Values",
       color = "Group")
```

## Comment
In general, the experimental group has a higher values compared to control group.


# Problem 3

## Set design elements
```{r}
sim = function(n = 30, mu = 0, sigma = 5) {

    x = rnorm(n = n, mean = mu, sd = sigma)

    t_result = 
      t.test(x, mu = mu) |>
      broom::tidy()
    
    sim_df =
      tibble(
        t_value = t_result$statistic,
        p_value = t_result$p.value,
        mean_hat = mean(x),
        sd_hat = sd(x)
      )
}

```

## Generated 5000 dataset
```{r}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:5000
  ) |> 
  mutate(
    estimate_df = map(sample_size, sim)
  ) |> 
  unnest(estimate_df)

head(sim_results_df)
```

## Repeated i mu = {1,2,3,4,5,6}
```{r}

```

